HAMdetector: A Bayesian regression model that integrates information to detect HLA-associated mutations

### 2021-02-21 docs/main.tex
worked through results

There is a range of sparsity-promoting priors with slightly different properties. They share the common structure of placing most probability mass very close to 0, with heavy tails to accommodate the non-zero coefficients.
For our model, we use a so-called horseshoe prior \citep{Carvalho2010}, a scale-mixture of Gaussians:
\begin{align}
  \label{eq:sparsity-prior}
  \begin{aligned}
    \beta_{jk} &\sim \text{Normal}(0, \tau^{2}\lambda^{2}_{jk}) \\
    \lambda_{jk} &\sim \text{Cauchy}^{+}(0, 1) \\
    \tau &\sim \text{Cauchy}^{+}(0, \tau_{0}),
  \end{aligned}
\end{equation}
where \(\beta_{jk}\) are the regression coefficients; \(\tau\) and \(\lambda_{jk}\) are the so-called global and local shrinkage parameters, respectively;, \(\text{Cauchy}^{+}\) is the positively constrained Cauchy distribution; $\tau_0$ is the overall degree of sparsity.

@@

The full specification of the model is:

@@

First, we checked with \emph{calibration plots} whether the inferred probabilities \(P(y_{ik}=1|\Psi)\) faithfully reflect the observed data (Fig.~\ref{fig:calibration}). All observations were binned according to their inferred probability \(P(y_{ik}=1|\Psi)\). If these probabilities are calibrated correctly, we expect that in a group of observations with an inferred probability \(P(y_{ik}=1|\Psi)\) of around x\% we really do observe \(y_{ik}=1\) around x\% percent of the time.

@@

In order to evaluate each building block of HAMdetector, we applied 4 different Bayesian models to each dataset, each of which includes the previous model as a special case:
A standard logistic regression model, a logistic regression model with horseshoe prior, a model additionally including phylogeny and the full model with horseshoe prior, phylogeny and epitope prediction.
As a comparison to existing methods, we also applied Fisher's exact test and the Phylogenetic Dependency Network.

\subsection{Model diagnostics}
\subsubsection{Convergence}
 All model fits showed no signs of inference issues. In total, samples were drawn from 4 different chains with 1000 iterations each. The effective sample size exceeded 500 for all model parameters, \(\hat{R}\) convergence diagnostic values were below 1.01 in all cases. \hl{DaHo: citation Gelman + Rubin original paper or later versions if improved $\hat{R}$ have been used}

\subsubsection{Calibration}

\subsection*{Posterior predictive checks}

Figure~\ref{fig:calibration} compares the calibration of the posterior predictive probability of observing the replacement to the actual observed data for the Core protein of the HBV dataset. Plots for the other models and datasets are shown in the supplementary.

The plots are similar to the one showed in figure~\ref{fig:phylogeny-calibration}, however, they do not evaluate the probabilities based on the phylogenetic model alone, but instead show the calibration of the posterior predictive probabilities based on the full model.

\begin{figure}[!ht]
  \includegraphics[width=1\linewidth]{plots/phylogeny_calibration.pdf}
  \caption{Calibration plot for the HBV dataset. Calibration plots for the other datasets are shown in the supplementary.
  All observations are first sorted by increasing estimated probability \(P(y_{ik}=1)\) and then grouped into \(n\) bins.
  For each bin, the fraction of observations with \(y_{ik}=1\) (observed event percentage) is compared to the midpoint of each bin (the value in the center between the lowest and highest probability). The error bars show the cutpoints for each bin. If the probabilities are calibrated correctly, each dot is supposed to scatter closely around the diagonal line.}
  \label{fig:calibration}
\end{figure}

\subsection{Comparison to a list of known epitopes}

@@

\begin{figure}[ht!]
  \includegraphics[width=1\linewidth]{plots/comparison.pdf}
  \caption{HAM enrichment plot for HBe protein: number $N_e$ of associations inside the boundary of known epitopes vs.\ rank $r$. PhyloD: Phylogenetic Dependency Network; model 1: simple logistic regression model with broad Student-t priors; model 2: logistic regression model with horseshoe prior; model 3: logistic regression model with horseshoe prior and phylogeny; model 4: full model with epitope prediction. The thin gray line are HAM enrichment curves for random permutations of the list of HLA allele - replacement pairs and act as baseline.}
  \label{fig:comparison}
\end{figure}

Figure~\ref{fig:comparison} shows a comparison of different models on the HBe protein of the HBV dataset. Plots for all other datasets are shown in the supplementary, but show identical patterns.

All models show a strong enrichment of HLA-associated mutations compared to a randomly permuted list of HLA allele - replacement pairs (gray lines). Fisher's exact test performs about as well as the simple logistic regression model, as from a statistical perspective, they are both similar.
The horseshoe prior alone is a drastic improvement over Fisher's exact test and the logistic regression model with non-sparsifying priors, even though it does not include any external information. The benefit comes from including the assumption that most regression coefficients are expected to be very close to 0.
The logistic regression model with horseshoe prior works roughly as well as the Phylogenetic Dependency Network, which includes much more information.
Note that the line for the Phylogenetic Dependency Network is shorter because it only outputs associations with a q-value lower than 0.2 by default.

The remaining models are ranked in order of the number of additional features they include. Additionally including phylogeny is a small improvement over the model with the horseshoe prior, while adding epitope prediction provides another strong improvement.

Note that this model only uses epitope \textit{prediction} software and does not use any information of experimentally confirmed epitopes. These are here only used for model evaluation.

Figure~\ref{fig:horseshoe-comparison} shows a comparison of marginal posteriors for regression coefficients with and without horseshoe prior.

Supplying information about the expected degree of sparsity with the horseshoe prior is a considerable improvement over a standard logistic regression model  (section~\ref{sec:results}).

\begin{figure}
  \includegraphics[width=1\linewidth]{plots/without_horseshoe.pdf}
  \includegraphics[width=1\linewidth]{plots/with_horseshoe.pdf}
  \caption{Marginal posterior distributions of a subset of regression coefficients for replacement 11D of the HIV integrase, based on the Arevir dataset. The graphic shows regression coefficients for two HLA alleles: For HLA-A*01, the data does not show evidence of an association with replacement 11D, whereas for HLA-B*44, the data is consistent with a strong association. The horseshoe prior has the effect of shrinking regression coefficients with weak evidence of an association with the replacement strongly towards 0, while leaving the coefficients that are far away from 0 mostly unshrunk. Shrinking the irrelevant regression coefficients to 0 has the advantage of reducing the standard error for the remaining coefficients, which can be observed by the much smaller width of the histogram of HLA-B*44 in the model with horseshoe prior.}
  \label{fig:horseshoe-comparison}
\end{figure}

@@

Table \ref{loo} shows a comparison of models with increasing complexity run on the HBe protein in the HDV dataset.

\begin{table}[h!]
  \renewcommand{\arraystretch}{1.3}
  \centering
  \caption{Differences in elpd for models with increasing model complexity (HBe protein of the HBV dataset).
  The numbers in column \(\text{elpd}_\text{diff}\) show increases in elpd compared to the previous model (higher is better), e.g. the difference in elpd of the model with horseshoe prior is 949.8 compared to the baseline model, and the difference in elpd for the model with phylogeny and horseshoe prior is 4440.9 compared to the model just with the horseshoe prior. All differences in elpd are larger than several times the estimated standard error (column \(\text{se}_\text{diff}\)), indicating that models which account for more information are expected to have a better predictive performance.}
  \vspace{0.5cm}
  \begin{tabular}{l|r|rll}
  \multicolumn{1}{l|}{} & \multicolumn{1}{c|}{\(\text{elpd}_\text{diff}\)} & \multicolumn{1}{c}{\(\text{se}_\text{diff}\)} &  &  \\ \cline{1-3}
  logistic regression (baseline) & 0.0  & 0.0 &  &  \\
  + horseshoe prior     & 949.8  & 65.2 &  &  \\
  + phylogeny & 4440.9 & 94.4 &  &  \\
  + epitope prediction & 63.1   & 18.9 &  & 
  \end{tabular}
  \label{loo}
\end{table}

Predictive accuracy increases as the models include more and more information.
Note that the model with horseshoe prior alone already has a much higher elpd than the standard logistic regression model, even though it does not use any additional external data. This is because including the sparsity assumption allows the model to better separate signal from noise and the uncertainty of the close-to-zero coefficients does not propagate into uncertainty of the estimated y.

Including phylogeny further improves model performance, as the assumption of independent and identically distributed data does not hold for sequence data that share a common phylogenetic history.

Inclusion of epitope prediction does not improve elpd as much as inclusion of phylogeny and the sparsity assumption. This is because while addition of sparsity and phylogeny has an effect on all replacements and samples, epitope prediction only influences those replacements which are restricted by a given HLA allele and only those samples which are annotated with the allele. However, inclusion of epitope prediction is highly useful for determining which HLA alleles are associated with the occurrence of a replacement, as shown in the previous section.

\hl{DaHo: Textblock aus alten Methods:}  We show that a simple logistic regression model with a sparsity-promoting prior on the regression coefficients for the HLA alleles alone already performs roughly on-par  with the much more elaborate Phylogenetic Dependency Network approach from Carlson et al. when using the fraction of identified escapes that lie in known HLA epitopes as a benchmark.

\subsection{Generalization}

\hl{DaHo: Es gibt fast keinen Text in dieser subsection}

The models were applied on sequence data from a variety of different viruses and show a considerable improvement over currently applied methods that are consistent across datasets.
These results are not due to overfitting, because leave-one-out cross-validation approximates the model performance on unseen data.

\subsection{Example Hepatitis Delta Virus}

We had the opportunity to test our model against a set of associations identified by Fisher's exact test where some of them turned out to be false positives~\cite{Karimzadeh2019}. This data is rare because negative results are usually not published in the literature, but provide a useful way to access model performance.
A comparison with a preliminary version of HAMdetector was published recently. Here we provide a comparison with results from Fisher's exact test~\cite{Budeus2016} and the mature version of HAMdetector used in this work.

Fisher's exact test and HAMdetector were applied to the same data (table~\ref{tab:false-positives}).
The posterior probabilities given by HAMdetector denote the probability that the corresponding regression coefficient is positive. Associations with strong support in our model have a posterior probability close to 1, associations with no support a probability close to 0.5 (corresponding to a regression coefficient centered around 0).

The results show low posterior probabilities for most of the false-positives and high posterior probabilities for most replacements that could be experimentally validated in IFN-\(\gamma\) production assays.
One important exception is P89T~-~HLA-B*37, which was experimentally validated but does not have strong support in our model.

\begin{table}[h!]
  \caption{List of HLA associated mutations that were identified using Fisher's exact test (FET). Experimental validation showed that 9 out of 15 replacements could not be experimentally validated (column “confirmed“). The data were re-analyzed using HAMdetector. Except for P89T, all validated replacements have high posterior probabilities, while the replacements that could not be experimentally validated have lower evidence of being HLA associated. Note that all replacement - HLA allele pairs had low p-values using Fisher's exact test.}
  \vspace{0.5cm}
  \begin{tabular}{c|c|c|c|c}
  replacement & allele  & p-value (FET) & post.~prob. & confirmed \\
  \hline
  S170N       & B*15 & \(3\cdot10^{-8}\)      & 0.99                                & +                        \\
  D101E       & B*37 & 0.0002                        & 0.96                                & +                        \\
  R105K       & B*27 & 0.0011                        & 0.93                                & +                        \\
  R139K       & B*41 & 0.0034                        & 0.91                                & +                        \\
  E47D        & B*18 & 0.0027                        & 0.89                                & +                        \\
  D33E        & B*13 & 0.0001                        & 0.86                                & -                        \\
  T134A       & A*68 & 0.0045                        & 0.82                                & -                        \\
  K43R        & B*13 & 0.0021                        & 0.77                                & -                        \\
  D47E        & A*30 & 0.0010                        & 0.76                                & -                        \\
  K113R       & B*13 & 0.0043                        & 0.76                                & -                        \\
  P89T        & B*37 & 0.0011                        & 0.75                                & +                        \\
  A107T       & B*14 & 0.0028                        & 0.70                                & -                        \\
  P49L        & A*30 & 0.0031                        & 0.63                                & -                        \\
  Q100L       & B*13 & 0.0018                        & 0.61                                & -                        \\
  D96E        & B*13 & 0.0035                        & 0.50                                & -                       
  \end{tabular}
  \label{tab:false-positives}
 \end{table}

 \subsection{Individual examples}
In the following we illustrate with ... examples the effects of the inclusion of additional relevant information on the detection of HAMs.

@@

\hl{DaHo: bitte konkretes Bsp mit Auswirkung Phylogenie zeigen}

@@

A straight-forward extension of our model would be to also account for these sources of uncertainty, for example by using a Bayesian method to estimate a posterior distribution over possible tree topologies. The uncertainty over the tree topology and the underlying parameters of the phylogenetic model would then propagate into uncertainty of the estimated probabilities \(P(y_{ik}=1|\Psi)\). However, in order to not increase the runtime of the model further we use standard maximum likelihood estimates and then include these in a way that additionally allows for measurement error.

>>>>

There is a range of sparsity-promoting priors with slightly different properties. They share the common structure of placing most probability mass very close to 0, with heavy tails to accommodate the non-zero coefficients.
For our model, we use a so-called horseshoe prior \citep{Carvalho2010}, a scale-mixture of Gaussians:
\begin{equation}
  \label{eq:sparsity-prior}
  \begin{aligned}
    \beta_{jk} &\sim \text{Normal}(0, \tau^{2}\lambda^{2}_{jk}) \\
    \lambda_{jk} &\sim \text{Cauchy}^{+}(0, 1) \\
    \tau &\sim \text{Cauchy}^{+}(0, \tau_{0}),
  \end{aligned}
\end{equation}
where \(\beta_{jk}\) are the regression coefficients; \(\tau\) and \(\lambda_{jk}\) are the so-called global and local shrinkage parameters, respectively;, \(\text{Cauchy}^{+}\) is the positively constrained Cauchy distribution; $\tau_0$ is the overall degree of sparsity.

@@

The full specification of the HAMdetector model is:

@@

For a first posterior predictive check we used \emph{calibration plots}: two binned quantities were plotted against each other, the observed relative frequencies of replacements $f(y_{ik}=1)$, and the predicted probabilities $P(y_{ik}=1|\text{model})$. In such a plot, a well-calibrated model should yield points following the diagonal. Technically, all observations were first sorted by increasing estimated probability $P(y_{ik}=1|\text{model})$ and grouped into $n$ bins. For each bin, the fraction of observations with $y_{ik}=1$ (observed event percentage) was then plotted against the midpoint of each bin. The cutpoints of the bins are indicated by error bars.
% We applied calibration plots twice, first with the phylogenetic component of model, and then with the full model.

@@

In order to understand what the different building blocks of HAMdetector contribute, we applied four different Bayesian models of increasing complexity to each dataset, starting with the standard logistic regression model (Eq~\ref{eq:backbone}), and adding then the further components, i.e.\ the horseshoe prior (Eq~\ref{eq:sparsity-prior}), phylogeny (Eq~\ref{eq:phylogeny}), and epitope prediction, resulting in the full model (Eq~\ref{eq:full}). For comparisons to existing methods, we also applied Fisher's exact test and the Phylogenetic Dependency Network \cite{Carlson2008} to the same data.

\subsection{Run times and convergence}
Run times of HAMdetector on a ... were of the order of ... \hl{DaHo: bitte ergänzen}
All model fits showed no signs of inference issues. In total, samples were drawn from four Hamiltonian Markov chains with 1000 iterations each after 1000 warm-up iterations. The effective sample size exceeded 500 for all model parameters, $\hat{R}$ convergence diagnostic values were below 1.01 in all cases.

\subsection{Posterior predictive checks}
The model yields well-calibrated posterior predictive probabilities of replacements. This is exemplified in Figure~\ref{fig:calibration} for HBV core protein, but also holds true for the other datasets (Supplementary Figures \hl{XXX-YYY}).

\begin{figure}[!ht]
 \includegraphics[width=1.0\linewidth]{plots/phylogeny_calibration.pdf}  
  \caption{Calibration plot for the HBV core protein.}
  \label{fig:calibration}
\end{figure}

@@

The predictions of all tested models are strongly enriched in epitopes over baselines, irrespective of dataset (Fig.~\ref{fig:comparison} for HBe protein and Supplementary Figures \hl{XXX-YYY} for other datasets). For the best ranked HAMs, Fisher's exact test performs about as well as the HAMdetector backbone logistic regression model (model 1 in Fig.~\ref{fig:comparison}). Each of the following three model stages of HAMdetector increases HAM enrichment further, independently of the dataset.
The horseshoe prior alone (model 2) is a drastic improvement over model 1, even though it does not include any external information. The logistic regression model with horseshoe prior works roughly as well as the Phylogenetic Dependency Network \cite{Carlson2008}, which includes much more information. Note that the line for the Phylogenetic Dependency Network is shorter because it only outputs associations with a q-value lower than 0.2 by default. Model 3 with its additional inclusion of phylogeny has higher enrichment than model 2, and finally, the full model 4 with the inclusion of epitope prediction leads to a further improvement. Note that model 4 only uses epitope \textit{prediction} software and does not use any information of experimentally confirmed epitopes. These are here only used for model evaluation.

\begin{figure}[ht!]
  \includegraphics[width=1\linewidth]{plots/comparison.pdf}
  \caption{HAM enrichment plot for HBe protein: number $N_e$ of associations inside the boundary of known epitopes vs.\ rank $r$. PhyloD: Phylogenetic Dependency Network; model 1: simple logistic regression model with broad Student-t priors; model 2: logistic regression model with horseshoe prior; model 3: logistic regression model with horseshoe prior and phylogeny; model 4: full model with epitope prediction. Gray lines are HAM enrichment curves for random permutations of the list of HLA allele - replacement pairs and act as baselines.}
  \label{fig:comparison}
\end{figure}

The Bayesian approach lends itself to addition of prior knowledge, and it is not too surprising that exploiting this feature to incorporate information from phylogeny or epitope prediction improves HAM detection. It may be more surprising that the sparsifying horseshoe prior has such an impact. However, this is in principle the same mechanism as for the other information components: it is known that HAMs are sparse per HLA allele, and therefore supplying this information to the inference improves predictions. Figure~\ref{fig:horseshoe-comparison} illustrates the effect of the sparsifying prior with a concrete example, the replacement 11D in HIV integrase (Arevir dataset). There is no evidence for an association of HLA-A*01 with this replacement, whereas for HLA-B*44 the data is consistent with a strong association.  The horseshoe prior has the effect of shrinking towards 0 specifically those regression coefficients with weak evidence of an association (A*01 in Fig.~\ref{fig:horseshoe-comparison}). This reduces the standard error for the remaining coefficients, leading in our example to narrowed histogram for the association with B*44 in the model with horseshoe prior.

\begin{figure}
  \includegraphics[width=1\linewidth]{plots/without_horseshoe.pdf}
  \includegraphics[width=1\linewidth]{plots/with_horseshoe.pdf}
  \caption{Marginal posterior distributions of regression coefficients for the association of replacement 11D of the HIV integrase with HLA alleles A*01 and B*44. Top half: inferred with logistic regression model, bottom half: inferred with logistic regression with sparsifying horseshoe prior.}
  \label{fig:horseshoe-comparison}
\end{figure}

@@

To quantify the ability of the four different model stages of HAMdetector to generalize to unseen cases, we computed the ELPD with Pareto-smoothed leave-one-out cross-validation. Table \ref{loo} shows results for the HBe protein of the HBV dataset in terms of ELPD changes with each new model stage. Each new model stage adds ELPD, i.e.\ is better at generalizing than the simpler model stages.

\begin{table}[h!]
  \renewcommand{\arraystretch}{1.3}
  \centering
  \caption{ELPD changes as HAMdetector components are added. Data computed for HBe protein of the HBV dataset. All differences in ELPD are larger than several times the estimated standard error (column \(\text{se}_\text{diff}\)), indicating that models that include more information have better predictive performance.}
  \vspace{0.5cm}
  \begin{tabular}{l|r|rll}
  \multicolumn{1}{l|}{} & \multicolumn{1}{c|}{\(\text{ELPD}_\text{diff}\)} & \multicolumn{1}{c}{\(\text{se}_\text{diff}\)} &  &  \\ \cline{1-3}
  logistic regression (baseline) & 0.0  & 0.0 &  &  \\
  + horseshoe prior     & 949.8  & 65.2 &  &  \\
  + phylogeny & 4440.9 & 94.4 &  &  \\
  + epitope prediction & 63.1   & 18.9 &  & 
  \end{tabular}
  \label{loo}
\end{table}

The model with horseshoe prior alone already has a much higher elpd than the standard logistic regression model, even though it does not use any specific external data. This is because including the sparsity assumption allows the model to better separate signal from noise and the uncertainty of the close-to-zero coefficients does not propagate into uncertainty of predictions.

Including phylogeny further improves model performance a lot, as the assumption of independent and identically distributed data is replaced with specific information from the shared phylogenetic history.

While addition of sparsity and phylogeny has an effect on all replacements and samples, epitope prediction only influences those replacements that are restricted by a given HLA allele and only those samples that are annotated with the allele. Therefore, inclusion of epitope prediction does not improve ELPD as much as inclusion of phylogeny and the sparsity assumption. However, inclusion of epitope prediction is highly useful for determining which HLA alleles are associated with a replacement, as shown in the previous section.

\subsection{HAMs in HDV as test case}
The Hepatitis D Virus (HDV) dataset \citep{Karimzadeh2019} is an excellent test case: we have (1) a set of paired HDV sequences and patient HLA alleles, (2) HAM predictions by Fisher's exact test as implemented in SeqFeatR \citep{Budeus2016}, and (3) experimental tests of the predicted HAMs for immune escape activity (IFN-\(\gamma\) production assays, \citet{Karimzadeh2019}). This allows us to see whether HAMdetector decreases the false positive rate in comparison to the simpler Fisher's exact test, and we can make \emph{bona fide} predictions on previously undetected HAMs. \hl{DaHo: zu \emph{bona fide}: können wir dazu etwas sagen? Ich erinnere mich, dass Du noch eine Reihe guter HAMs vorhergesagt hattest.}

We have 15 HAMs predicted in HDV by Fisher's exact test at significance level $5\times 10^{-3}$ (Table~\ref{tab:false-positives}) as published \citep{Karimzadeh2019}. The corresponding p-values  have no clear relation to experimental confirmation, i.e.\ p-values for confirmed HAMs are not generally lower than those of non-confirmed ones.

For HAMdetector, we use in Table~\ref{tab:false-positives} the posterior probability of a positive regression coefficient ($P(\beta_{\text{HLA}_{jk}}>0)$ as measure for the confidence in having detected a HAM. HAMs with strong support have a posterior probability close to 1, associations with no support a probability close to 0.5 (corresponding to a regression coefficient centered around 0). The five predicted HAMs with top posterior probabilities (all $\ge 0.89$) have all been experimentally confirmed. There is only one outlier with posterior probability 0.75 (P89T and B*37).

\begin{table}[h!]
  \caption{List of HAMs predicted Fisher's exact test (FET). In the last column a ``+'' marks experimental confirmation and a ``-'' a failed confirmation. Column ``post.prob.'' shows the corresponding posterior probabilities for positive associations computed with HAMdetector.}
  \vspace{0.5cm}
  \begin{tabular}{c|c|c|c|c}
  replacement & allele  & p-value (FET) & post.~prob. & confirmed \\
  \hline
  S170N       & B*15 & $3\cdot10^{-8}$      & 0.99                                & +                        \\
  D101E       & B*37 & 0.0002                        & 0.96                                & +                        \\
  R105K       & B*27 & 0.0011                        & 0.93                                & +                        \\
  R139K       & B*41 & 0.0034                        & 0.91                                & +                        \\
  E47D        & B*18 & 0.0027                        & 0.89                                & +                        \\
  D33E        & B*13 & 0.0001                        & 0.86                                & -                        \\
  T134A       & A*68 & 0.0045                        & 0.82                                & -                        \\
  K43R        & B*13 & 0.0021                        & 0.77                                & -                        \\
  D47E        & A*30 & 0.0010                        & 0.76                                & -                        \\
  K113R       & B*13 & 0.0043                        & 0.76                                & -                        \\
  P89T        & B*37 & 0.0011                        & 0.75                                & +                        \\
  A107T       & B*14 & 0.0028                        & 0.70                                & -                        \\
  P49L        & A*30 & 0.0031                        & 0.63                                & -                        \\
  Q100L       & B*13 & 0.0018                        & 0.61                                & -                        \\
  D96E        & B*13 & 0.0035                        & 0.50                                & -                       
  \end{tabular}
  \label{tab:false-positives}
 \end{table}

 \subsection{Linkage disequilibrium}

@@

@@

A straightforward extension of our model would be to also account for these sources of uncertainty, for example by using a Bayesian method to estimate a posterior distribution over possible tree topologies. The uncertainty over the tree topology and the underlying parameters of the phylogenetic model would then propagate into uncertainty of the estimated probabilities \(P(y_{ik}=1|\Psi)\). However, in order to not increase the runtime of the model further we use standard maximum likelihood estimates and then include these in a way that additionally allows for measurement error.
